---
title: "Assignments"
format: 
  html: 
    toc: true
    embed-resources: true
execute:
  echo: false
  warning: false
---

```{r}
#| include: false
#| message: false

# library(tidyverse)
# library(here)
# library(readxl)
# library(fontawesome)
library(gt)
library(xfun)
library(htmltools)
# library(mime)

table_style <- function(data) {
  data |> 
    opt_table_lines(extent = "none") |> 
    opt_table_outline(style = "solid", width = px(3), color = "black") |> 
    tab_options(
      heading.border.bottom.color = "black",
      heading.border.bottom.style = "solid",
      table.border.top.color = "black",
      table_body.hlines.color = "black",
      table_body.border.top.color = "black",
      table_body.border.top.style = "solid",
      table_body.border.bottom.color = "black",
      table_body.border.bottom.style = "solid",
      column_labels.border.bottom.color = "black",
      column_labels.border.bottom.style = "solid",
      column_labels.border.top.color = "black",
      column_labels.background.color = "#03396a",
      table.width = pct(100),
      container.width = pct(100)
    )
}
```

As listed in the [Syllabus](w26syllabus.qmd), the following assignments will largely take place in class, with a few supplemental materials being turned in via Moodle. Each assignment is outlined in detail below.

```{r}
tibble::tribble(
  ~Assignments, ~Points,
  "Syllabus Quiz", 10L,
  "Lecture Quizzes", 80L,
  "Speech Analyses", 50L,
  "\"Tell Me About Yourself\" Speech", 25L,
  "Informative Speech", 100L,
  "Informative Speech Critiques", 30L,
  "Impromptu Speech", 20L,
  "Advocacy Speech", 100L,
  "Advocacy Speech Critiques", 30L,
  "\"Nostalgia\" Speech", 25L,
  "Commitment", 30L,
  "Total", 500L
) |> 
  gt() |>
  tab_style(
    style = cell_borders(
      sides = "top",
      color = "black",
      weight = px(1)
    ),
    locations = cells_body(
      rows = Assignments == "Total"
    )
  ) |>
  tab_style(
    style = cell_text(
      weight = "bold",
      style = "italic"
      ),
    locations = cells_body(
      rows = Assignments == "Total"
    )
  ) |> 
  table_style()
```

## Syllabus Quiz

This assignment is meant to familiarize you with the expectations of the course and give me a chance to get a brief bit of insight into what you are bringing to the classroom discourse in terms of existing interests and experiences with public speaking. This will occur in class during Week 1.

## Lecture Quizzes

These are meant to assess basic comprehension of concepts related to public speaking as covered in your weekly lecture material. These quizzes will each be a few questions containing a mixture of multiple choice, true or false, and short answer questions. Quizzes will be open-note and open-lecture slides, meaning you have access to any and all resources except for the students sitting around you. Five of these quizzes will occur during the term; only your highest **four** scores will be kept. These will occur in class at undisclosed periods throughout the term.

## Speech Analyses

These analyses will give you an opportunity to critique the elements of public speaking you have been learning about. You will be provided with a selection of speeches to choose from and key elements for you to analyze in the presentation, highlighting the strengths and weaknesses contained in the speech. Your analysis should be no more than 2 pages, double-spaced, in 12-point font. These will be due at the end of Weeks 4 and 10.

## "Tell Me About Yourself" Speech

At some point in your life, you will hear these words from an employer, a date, a stranger, or any other potential person of interest or import. This speech is your opportunity to perfect your 60-second summary of who you are. Where are you from? What do you do (or plan to do) for work? What are your greatest passions? The pitch differs from person to person, but ultimately, this speech helps you be prepared for the inevitable. These speeches do not require an outline or virtual submission and will be done in class during Week 3.

## Impromptu Speech

Being put on the spot is never fun, but it's better to get a taste of it in a controlled environment like the classroom. At some point in the term, you will be expected to give an impromptu speech. I will tell you the day it is set to happen, but not the subject on which you are giving the speech. It will be relatively low stakes, no more than 1 minute in length, and will not require any sort of outline or virtual submission, but you **must** be in attendance on the day speeches happen in order to earn credit.

## "Nostalgia" Speech

Everyone has a story that takes them back — a moment, place, or experience that sparks a feeling of nostalgia. This brief speech is your opportunity to revisit one of those moments and share it with your audience in an entertaining way. This speech will be no more than 2 minutes in length, will not require an outline or virtual submission, and will be done in class during Week 10.

## Informative Speech

With this speech, you are now the expert on something, and your audience needs to learn about it. Perhaps there is an endangered species you think deserves greater attention, a recent change to a small town that is impacting its residents, or shifts in public expectations of politicians, politics, and policy. You decide the topic and demonstrate to us that you understand it effectively enough to inform us about it. This speech should be about 5 minutes in length. You will submit an outline virtually for the speech that **must** follow the provided outline format; submitting a manuscript of your speech will result in a point deduction. These speeches will take place in class during Week 6.

## Informative Speech Critiques

Being able to evaluate a speech is just as important as being able to deliver one. What areas of a speech stood out? Which areas fell flat? What did the presenter do well? Where can they improve? As part of your critique, you will evaluate performative criteria (i.e., the speaker's volume, their eye contact, their posture, etc.) and content criteria (i.e., the organization of material, the use of evidence, the speaker's preparedness, etc.). Your evaluation will not factor into the speaker's grade, but you are required to do evaluations of **two** other students' speeches. These evaluations will take place during Week 6 and be due as virtual submissions by the end of Week 6.

## Advocacy Speech

Your previous speech was meant to inform; now you are to advocate. Much like a persuasive speech, this is your opportunity to display your passion for something and advocate for meaningful change. Maybe you believe public schools should receive more funding, or private prisons should be abolished, or space exploration should be prioritized. This is your chance to demonstrate passion and attempt to convince the audience that the current status quo should be changed in favor of what you are advocating for. This speech will use evidence to support your claim and will similarly demonstrate your understanding and vested interest in the subject. This speech should be about 5 minutes in length. You will submit an outline virtually that includes a References page. These speeches will take place during Week 9.

## Advocacy Speech Critiques

As with the informative speeches, you will once again be required to evaluate the speeches of your peers, this time to assess areas of strength and weakness as they pertain to the speaker's ability to clearly and effectively convey their argument. You will again evaluate performative criteria (i.e., the speaker's volume, their eye contact, their posture, etc.) and content criteria (i.e., the organization of material, the use of evidence, the speaker's preparedness, etc.), while also offering insight on if you believe the argument achieved certain criteria that will be outlined in the evaluation document. Your evaluation will not factor into the speaker's grade, but you are required to do evaluations of **two** other students' speeches. These evaluations will take place during Week 9 and will be due as virtual submissions by the end of Week 9.

## Commitment

Commitment is difficult to comprehensively describe while simultaneously being painfully obvious. By being **committed** to the course, you are going one step further than simply showing up. You are dedicated to helping foster a productive and engaging shared learning environment. This means actively participating and providing thoughtful contributions to discussions and activities, coming prepared by finishing readings and remaining engaged throughout the class period, respecting the perspectives and ideas of your peers, and maintaining a level of professionalism throughout. In a class focused on communication, I expect you to play a role in the discourse we will inevitably explore as we work to collaboratively address areas we know and care about. This grade rewards those who actively contribute to the collective success of the class.