---
title: "Schedule"
format: 
  html: 
    css:
      - styles.css
      - styles-schedule.css
    toc: true
    embed-resources: true
    include-after-body:
      - text: |
          <script>
          document.addEventListener("DOMContentLoaded", function () {
            document
              .querySelectorAll('a[href^="http"]:not([href^="' + window.location.origin + '"])')
              .forEach(a => {
                a.setAttribute("target", "_blank");
                a.setAttribute("rel", "noopener");
              });
          });
          </script>
execute:
  echo: false
  warning: false
---

```{r}
#| include: false
#| message: false

library(gt)
library(tibble)

```

This page will be updated regularly to include links to assignment submission pages, which includes assignment-specific information, as well as to have accessible lecture slides for you to review.

### Week 1: Thinking About Public Speaking

```{r}
#| label: week-1

schedule <- tibble(
  Content = "Introduction to the Course; Why Public Speaking Matters; Ethics; Speaking Confidently",
  Lectures = "[The Bigger Questions of Public Speaking](classfiles/slides/week1day2.pdf)",
  Readings = paste0(
    '<u>*"Stand Up, Speak Out"*</u><br>',
    "Why Public Speaking <br>Matters - [Chapter 1](https://drive.google.com/open?id=1eW6GuodbB7qZsEVSWnib1mRyQp17ugeY)<br>",
    "Ethics - [Chapter 2](https://drive.google.com/open?id=1sRb372zzEWWy-RdT_mWUdemXfHlAjZqP)<br>",
    "Speaking Confidently - [Chapter 3](https://drive.google.com/open?id=1gqsEWOv-FgEgDhGCKi64mPayeCIAQ_yu)"
  ),
  Assignments = "[***Syllabus Quiz***](https://classes.lanecc.edu/mod/assign/view.php?id=4743212)"
)

schedule |>
  gt() |>
  fmt_markdown(columns = everything()) |> 
  cols_align(
    align = "left",
    columns = everything()
  )
```

### Week 2: Preparing to Speak

```{r}
#| label: week-2

schedule <- tibble(
  Content = c(
    "Listening; Audience Analysis; Language",
    ""
  ),
  Lectures = c(
    "[Listening as Part of Public Speaking](classfiles/slides/week2day1.pdf)",
    "[Audience Analysis, Values, and Language](classfiles/slides/week2day2.pdf)"
  ),
  Readings = c(
    paste0(
      '<u>*"Stand Up, Speak Out"*</u><br>',
      "Listening - [Chapter 4](https://drive.google.com/open?id=1vuKb_0PVgH7dC8n1xPZ2apZ7RcobbF99)<br>",
      "Audience Analysis - [Chapter 5](https://drive.google.com/open?id=1I76Wjvaxjapi1vBDQdbEfkkryICk_boV)<br>",
      "Language - [Chapter 13](https://drive.google.com/open?id=1aNMivE2Z900n7IMBEgj1nyezd695-VTB)"
    ),
    paste0(
      '<u>*"Exploring Public Speaking"*</u><br>',
      "Developing Topics <br>for Your Speech - [Chapter 4](https://drive.google.com/file/d/1BEW83Q-wO5zWvNBjHbf8-E4-U7qR5GpF/view?usp=drive_link)"
    )
  ),
  Assignments = c(
    "",
    ""
  )
)

schedule |>
  gt() |>
  fmt_markdown(columns = everything()) |> 
  cols_align(
    align = "left",
    columns = everything()
  )
```

### Week 3: Crafting Your Speech

```{r}
#| label: week-3

schedule <- tibble(
  Content = c(
    'Introductions; Body of the Speech; Conclusions; "Tell Me About Yourself" Speeches',
    ""
  ),
  Lectures = c(
    "[Structuring a Speech](classfiles/slides/week3day1.pdf)",
    "[Speaking with Confidence](classfiles/slides/week3day2.pdf)"
  ),
  Readings = c(
    paste0(
      '<u>*"Stand Up, Speak Out"*</u><br>',
      "Introductions - [Chapter 9](https://drive.google.com/open?id=1JlkUbxhh7kEw3jNVmiOoe_cpWl8q7mUx)<br>",
      "Body of the Speech - [Chapter 10](https://drive.google.com/open?id=1SS3Uzo2xSlr6VaAZpA_IXYsQQ7X-naP-)<br>",
      "Conclusions - [Chapter 11](https://drive.google.com/open?id=1ejqWi2KDb_d4-VGpVcQl1jxhggzrPSIO)"
    ),
    ""
  ),
  Assignments = c(
    '[***"Tell Me About Yourself" Speech***](https://classes.lanecc.edu/mod/assign/view.php?id=4743214)',
    ""
  )
)
schedule |>
  gt() |>
  fmt_markdown(columns = everything()) |> 
  cols_align(
    align = "left",
    columns = everything()
  )
```

### Week 4: Informative Speaking

```{r}
#| label: week-4

schedule <- tibble(
  Content = c(
    "Delivery; Informative Speaking",
    ""
  ),
  Lectures = c(
    "[Delivering Your Speech](classfiles/slides/week4day1.pdf)",
    "[Speaking to Inform](classfiles/slides/week4day2.pdf)"
  ),
  Readings = c(
    paste0(
      '<u>*"Stand Up, Speak Out"*</u><br>',
      "Delivery - [Chapter 14](https://drive.google.com/open?id=1UZw5UxrZNCRzVPHrla8_mzD0DP_eq2Cu)<br>",
      "Informative Speaking - [Chapter 16](https://drive.google.com/open?id=1YOpZI0MnfO6zrhyRzNAy4YNzJd9tBcA5)<br>"
    ),
    paste0(
      '<u>*"Exploring Public Speaking"*</u><br>',
      "Organizing and Outlining <br>Your Speech - [Chapter 6](https://drive.google.com/file/d/1YPnMB_lzVJGxckE_mxS2CYN7u9rJHpJP/view?usp=drive_link)"
    )
  ),
  Assignments = c(
    "[***Speech Analysis #1***](https://classes.lanecc.edu/mod/assign/view.php?id=4743218)",
    ""
  )
)

schedule |>
  gt() |>
  fmt_markdown(columns = everything()) |> 
  cols_align(
    align = "left",
    columns = everything()
  )
```

### Week 5: Research & Support

```{r}
#| label: week-5

schedule <- tibble(
  Content = c(
    "Research the Speech; Supporting Sides",
    ""
  ),
  Lectures = c(
    "[Researching the Speech](classfiles/slides/week5day1.pdf)",
    "Types of Evidence"
  ),
  Readings = c(
    paste0(
      '<u>*"Stand Up, Speak Out"*</u><br>',
      "Research the Speech - [Chapter 7](https://drive.google.com/open?id=1ASaNms2KmqJJxgINKQW4Xusz8V8trl0W)<br>",
      "Supporting Sides - [Chapter 8](https://drive.google.com/open?id=1rMcDiG_OyuLaPmKAk8urI2qfuZqTiS0P)<br>"
    ),
    ""
  ),
  Assignments = c(
    "",
    ""
  )
)

schedule |>
  gt() |>
  fmt_markdown(columns = everything()) |> 
  cols_align(
    align = "left",
    columns = everything()
  )
```

### Week 6: Informative Speeches

```{r}
#| label: week-6

schedule <- tibble(
  Content = c(
    "Informative <br>Speeches",
    ""
  ),
  Lectures = c(
    "No lecture material this week",
    ""
  ),
  Readings = c(
    "No readings this week",
    ""
  ),
  Assignments = c(
    "[***Informative Speech***](https://classes.lanecc.edu/mod/assign/view.php?id=4743486)",
    "[***Informative Speech Critiques***](https://classes.lanecc.edu/mod/assign/view.php?id=4743489)"
  )
)

schedule |>
  gt() |>
  fmt_markdown(columns = everything()) |> 
  cols_align(
    align = "left",
    columns = everything()
  )
```


### Week 7: Persuasive Speaking & Advocacy

```{r}
#| label: week-7

schedule <- tibble(
  Content = "Persuasive Speaking; Advocacy",
  Lectures = "Persuasion and Argumentation",
  Readings = paste0(
      '<u>*"Stand Up, Speak Out"*</u><br>',
      "Persuasive Speaking - [Chapter 17](https://drive.google.com/open?id=1iraqfwq5xyeKk3e_W5_GEH89EgqPUFKX)<br>"
    ),
  Assignments = ""
)

schedule |>
  gt() |>
  fmt_markdown(columns = everything()) |> 
  cols_align(
    align = "left",
    columns = everything()
  )
```

### Week 8: Structuring an Argument & Fallacies

```{r}
#| label: week-8

schedule <- tibble(
  Content = c(
    "Structuring an <br> Argument; Fallacies",
    ""
  ),
  Lectures = c(
    "Structuring Your Argument",
    "Fallacies in Argumentation"
  ),
  Readings = c(
    "No readings this week",
    ""
  ),
  Assignments = c(
    "",
    ""
  )
)

schedule |>
  gt() |>
  fmt_markdown(columns = everything()) |> 
  cols_align(
    align = "left",
    columns = everything()
  )
```

### Week 9: Advocacy Speeches

```{r}
#| label: week-9

schedule <- tibble(
  Content = c(
    "Advocacy <br>Speeches",
    ""
  ),
  Lectures = c(
    "No lecture material this week",
    ""
  ),
  Readings = c(
    "No readings this week",
    ""
  ),
  Assignments = c(
    "[***Advocacy Speech***](https://classes.lanecc.edu/mod/assign/view.php?id=4743491)",
    "[***Advocacy Speech Critiques***](https://classes.lanecc.edu/mod/assign/view.php?id=4743493)"
  )
)

schedule |>
  gt() |>
  fmt_markdown(columns = everything()) |> 
  cols_align(
    align = "left",
    columns = everything()
  )
```

### Week 10: Speaking to Entertain

```{r}
#| label: week-10

schedule <- tibble(
  Content = c(
    'Speaking to Entertain; "Nostalgia" Speeches',
    ""
  ),
  Lectures = c(
    "Entertainment as Communication",
    ""
  ),
  Readings = c(
    paste0(
      '<u>*"Stand Up, Speak Out"*</u><br>',
      "Speaking to Entertain - [Chapter 18](https://drive.google.com/open?id=1OGEm9RpdDy0iaMQ4FY7b9ttIxu1BE5Ap)<br>"
    ),
    ""
  ),
  Assignments = c(
    '[***"Nostalgia" Speech***](https://classes.lanecc.edu/mod/assign/view.php?id=4743497)',
    "[***Speech Analysis #2***](https://classes.lanecc.edu/mod/assign/view.php?id=4743500)"
  )
)

schedule |>
  gt() |>
  fmt_markdown(columns = everything()) |> 
  cols_align(
    align = "left",
    columns = everything()
  )
```

### Finals Week
::: {.schedule-tight}
```{r}
#| label: finals-week

schedule <- tibble(
  Content = "Finals Week",
  Lectures = "",
  Readings = "",
  Assignments = "***NOTHING. Happy Spring Break!***"
)

schedule |>
  gt() |>
  fmt_markdown(columns = everything()) |> 
  cols_align(
    align = "left",
    columns = everything()
  )
```
:::
***\*This schedule is tentative and subject to change at the instructor's discretion.***
